Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-09 ms.tex
rewriting introduction to reddening section

While the temperature and optical depth maps thus far derived are
useful for making thermal dust emission foreground predictions, estimating 
optical reddening/extinction is another important application of the 
$\tau_{545}$ map.

@@

We calibrate to reddening empirically rather than derive
a relationship between $\tau_{545}$ and reddening by introducing additional 
assumptions about the dust grain physics and size distribution. To achieve this
empirical calibration, we must adopt a set of calibrator objects for which true
optical reddening is known. There are various possibilities at our disposal. 
\cite{planckdust} calibrated their radiance and $\tau_{353}$ maps to $E(B-V)$ 
using broadband Sloan Digital Sky Survey \citep[SDSS;][]{sdss} photometry for a
set of $\sim$10$^5$ quasars. The SFD calibration was originally tied to a 
sample of 384 elliptical galaxies, but was later revised by 
\citet[hereafter SF11]{schlafly11} based on $\sim$260,000 stars with both 
spectroscopy and broadband photometry available from SDSS.

% maybe note the possibility in the future of calibrating to a 3D dust
% map type data product rather than directly to a set of individual 
% stars/galaxies

@@

\subsection{Towards a Replacement for SFD}
%  ---> CIBA
%   ---> do i want a figure illustrating the CIBA problem at high latitude ?
%  ---> zodi
%  ---> more testing needed, in any event, to prove Planck based reddening
%       estimates outperform SFD

>>>>

While the temperature and optical depth maps thus far derived are
useful for making thermal dust emission foreground predictions, estimating 
optical reddening/extinction is another important application of the 
$\tau_{545}$ map. Translating our two-component optical depth to reddening
is especially valuable because our $T_2$ map has $\sim$13$\times$ better
angular resolution than the SFD temperature correction, and thus there is 
reason to believe our two-component reddening estimates may be superior to
those of SFD. However, as discussed in $\S$\ref{sec:replace}, we do not yet 
advocate for the wholesale replacement of SFD, and more detailed work is still 
necessary to determine/quantify the extent to which \PLANCK-based dust maps
might improve reddening estimates relative to SFD.

@@

We calibrate optical depth to reddening empirically rather than derive a 
relationship between $\tau_{545}$ and reddening by introducing additional 
assumptions about the dust grain physics and size distribution. To achieve this
empirical calibration, we must adopt a set of calibrator objects for which true
optical reddening is known. There are various possibilities at our disposal. 
\cite{planckdust} calibrated their radiance and $\tau_{353}$ maps to $E(B-V)$ 
using broadband Sloan Digital Sky Survey \citep[SDSS;][]{sdss} photometry for a
set of $\sim$10$^5$ quasars. The SFD calibration was originally tied to a 
sample of 384 elliptical galaxies, but was later revised by 
\citet[hereafter SF11]{schlafly11} based on $\sim$260,000 stars with both 
spectroscopy and broadband photometry available from SDSS.

@@

\subsection{Towards a Replacement for SFD}
\label{sec:replace}
%  ---> CIBA
%   ---> do i want a figure illustrating the CIBA problem at high latitude ?
%  ---> zodi
%  ---> more testing needed, in any event, to prove Planck based reddening
%       estimates outperform SFD
